Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}

library(ggplot2)

getwd()
setwd("C:/Users/Usuario/Desktop")
list.files()

pf <- read.csv('pseudo_facebook.tsv', sep = '\t')

```

```{r}
qplot(x=age, y=friend_count, data=pf)

```

```{r}
qplot(age, friend_count, data=pf)

```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}

ggplot(aes(x=age, y=friend_count), data=pf) + geom_point()

```

```{r}

summary(pf$age)

```

```{r}

ggplot(aes(x=age, y=friend_count), data=pf) + geom_point() + xlim(13,90)

```


***

### Overplotting
Notes:

```{r Overplotting}

ggplot(aes(x=age, y=friend_count), data=pf) + 
  geom_point(alpha=1/20) + 
  xlim(13,90)

```


```{r}

ggplot(aes(x=age, y=friend_count), data=pf) + 
  geom_jitter(alpha=1/20) + 
  xlim(13,90)

```



#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}

ggplot(aes(x=age, y=friend_count), data=pf) + 
  geom_point(alpha=1/20 , position = position_jitter(h=0)) + 
  xlim(13,90) +
  coord_trans(y="sqrt")

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}

ggplot(aes(x=age, y=friendships_initiated), data=pf) +
  geom_point(alpha=1/10, position = position_jitter(h=0) ) +
  xlim(13,90) +
  coord_trans(y="sqrt")


```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}

install.packages('dplyr')
library(dplyr)

```

Create your plot!

```{r Conditional Means Plot}

age_groups <- group_by(pf,age)
pf.fc_by_age <- summarise(age_groups,
          friend_count_mean=mean(friend_count),
          friend_count_median = median(friend_count),
          n= n())

pf.fc_by_age <- arrange(pf.fc_by_age,age)

head(pf.fc_by_age)

```

```{r}

pf.fc_by_age <- pf %>%
  group_by(age) %>%
  summarise(friend_count_mean=mean(friend_count),
          friend_count_median = median(friend_count),
          n= n()) %>%
  arrange(age)

head(pf.fc_by_age,20)

```

```{r}

ggplot(aes(age, friend_count_mean), data=pf.fc_by_age,) + geom_line()

```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}

ggplot(aes(x=age, y=friend_count), data=pf) +
  geom_point(alpha=1/20, position = position_jitter(h=0), color='orange' ) +
  xlim(13,90) +
  coord_trans(y="sqrt") +
  geom_line(stat='summary', fun.y=mean) +
  geom_line(stat='summary', fun.y=quantile, fun.args= list(probs= 0.1), linetype=2,
            color='blue') +
  geom_line(stat='summary', fun.y=quantile, fun.args= list(probs= 0.5),
            color='green') +
  geom_line(stat='summary', fun.y=quantile, fun.args= list(probs= 0.9), linetype=2,
            color='red')


```

#### What are some of your observations of the plot?
Response:

```{r}

ggplot(aes(x=age, y=friend_count), data=pf) +
  geom_point(alpha=1/20, position = position_jitter(h=0), color='orange' ) +
  coord_cartesian(xlim=c(13,70), ylim=c(0,1000)) +
  coord_trans(y="sqrt") +
  geom_line(stat='summary', fun.y=mean) +
  geom_line(stat='summary', fun.y=quantile, fun.args= list(probs= 0.1), linetype=2,
            color='blue') +
  geom_line(stat='summary', fun.y=quantile, fun.args= list(probs= 0.5),
            color='green') +
  geom_line(stat='summary', fun.y=quantile, fun.args= list(probs= 0.9), linetype=2,
            color='red')


```


***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}

cor.test(x=pf$age,y=pf$friend_count, method = 'pearson')

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

```{r}

with(pf,cor.test(age,friend_count, method = 'pearson'))

```

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with( subset(pf,age<=70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

```{r}

with( subset(pf,age<=70), cor.test(age, friend_count, method='spearman'))

```

***

## Create Scatterplots
Notes:

```{r}

names(pf)

```

```{r}

ggplot(aes(x=likes_received, y=www_likes_received), data=pf) +
  geom_point(alpha=1/20, position = position_jitter(h=0)) +
  coord_cartesian(xlim=c(0,250), ylim=c(0,250)) +
  geom_line(stat='summary', fun.y=mean, color='orange')

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

ggplot(aes(x=likes_received, y=www_likes_received), data=pf) +
  geom_point() +
  xlim(0, quantile(pf$www_likes_received,0.95)) +
  ylim(0, quantile(pf$likes_received,0.95)) + 
  geom_smooth(method = 'lm', color = 'red')

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

with(pf,cor.test(likes_received,www_likes_received, method = 'pearson'))


```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)

data(Mitchell)
?Mitchell
```

```{r}

head(Mitchell)

```


Create your plot!

```{r Temp vs Month}

ggplot(aes(x=Month, y=Temp), data=Mitchell) +
  geom_point()


```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

with(Mitchell,cor.test(Month,Temp, method = 'pearson'))

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

ggplot(aes(x=Month, y=Temp), data=Mitchell) +
  geom_point() + 
  scale_x_discrete(breaks=seq(0,203,12))

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

```{r}

ggplot(aes(x=(Month%%12),y=Temp),data=Mitchell)+ 
  geom_point() 

```



***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

ggplot(aes(x=age, y=friend_count_mean), data=pf.fc_by_age) +
  geom_line()

head(pf.fc_by_age,10)
pf.fc_by_age[17:18,]

```

```{r}

pf$age_with_months <- pf$age + (12 - pf$dob_month) / 12

```


***

### Age with Months Means

```{r Age with Months Means}


pf.fc_by_age_months <- pf %>%
  group_by(age_with_months) %>%
  summarise(friend_count_mean=mean(friend_count),
          friend_count_median = median(friend_count),
          n= n()) %>%
  arrange(age_with_months)

head(pf.fc_by_age_months,10)

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

ggplot(aes(x=age_with_months, y=friend_count_mean), data=subset(pf.fc_by_age_months,age_with_months<71)) +
  geom_line()

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

p1 <- ggplot(aes(x=age, y=friend_count_mean), data=subset(pf.fc_by_age,age<71)) +
  geom_line()

p2 <- ggplot(aes(x=age_with_months, y=friend_count_mean), data=subset(pf.fc_by_age_months,age_with_months<71)) +
  geom_line()

p3 <- ggplot(aes(x=round(age/5)*5, y=friend_count), data=subset(pf,age<71)) +
  geom_line(stat='summary', fun.y = mean)

library(gridExtra)
grid.arrange(p2,p1,p3,ncol=1)

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

