Lesson 3
===================================================

##Reading Data

```{r}

getwd()
setwd("C:/Users/Usuario/Desktop")
list.files()

pf<-read.csv("pseudo_facebook.tsv", sep= "\t")


```

## Histogram of User's Birthday
```{r}
library(ggplot2)

names(pf)

qplot(x=dob_day, data=pf) +
  scale_x_continuous(breaks=1:31)


```

##Install ggthemes

```{r}

##install.packages('ggthemes', dependencies = TRUE) 
##library("ggthemes")

```

## Using Theme Minimal Font size 24

```{r}
theme_set(theme_minimal(24))
ggplot(aes(x = dob_day), data = pf) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31)

```

##Faceting
```{r}

qplot(x=dob_day, data=pf) +
  scale_x_continuous(breaks=1:31) +
  facet_wrap(~dob_month, ncol=3)

```




##Faceting in GGPLOT
```{r}

ggplot(data = pf, aes(x = dob_day)) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31) + 
  facet_wrap(~dob_month)

```

##Friend Count
```{r}

qplot(x=friend_count, data=pf)

```

##Limit the axes
```{r}

qplot(x=friend_count, data=pf, xlim=c(0,1000))

qplot(x=friend_count, data=pf) +
  scale_x_continuous(limits=c(0,1000))

```

##Adjusting then Bin Width
```{r}
qplot(x=friend_count, data=pf, binwidth=25) +
  scale_x_continuous(limits=c(0,1000), breaks=seq(0,1000,50))

```

##Faceting by gender
```{r}

qplot(x=friend_count, data=pf, binwidth=25) +
  scale_x_continuous(limits=c(0,1000), breaks=seq(0,1000,50)) +
  facet_wrap(~gender)

```

##Omitting NA gender Observations
```{r}

qplot(x=friend_count, data=subset(pf,!is.na(gender)), binwidth=25) +
  scale_x_continuous(limits=c(0,1000), breaks=seq(0,1000,50)) +
  facet_wrap(~gender)

```

```{r}

qplot(x=friend_count, data=na.omit(pf), binwidth=25) +
  scale_x_continuous(limits=c(0,1000), breaks=seq(0,1000,50)) +
  facet_wrap(~gender)

```

## Statistics 'by' Gender
```{r}

table(pf$gender)

```

```{r}

by(pf$friend_count, pf$gender,summary)

```

## Tenure
```{r}

qplot(x = tenure, data=pf, binwidth=30,
      color = I('black'), fill =I('#099DD9'))

```

## Tenure measured in years

```{r}

qplot(x = tenure/365, data=pf, binwidth=.25,
      color = I('black'), fill =I('#F79420')) +
  scale_x_continuous(limits=c(0,8))

```

## Labeling Plots

```{r}

qplot(x = tenure/365, data=pf, binwidth=.25,
      xlab= 'Number of years using Facebook',
      ylab= 'Number of users in sample',
      color = I('black'), fill =I('#F79420')) +
  scale_x_continuous(limits=c(0,7), breaks = seq(1,7,1))

```

## Histogram for Ages

```{r}

qplot(x = age, data=pf, binwidth=5,
      xlab= 'Age users in Facebook',
      ylab= 'Number of users in sample',
      color = I('black'), fill =I('blue')) +
  scale_x_continuous(limits=c(10,120), breaks = seq(10,120,10))

summary(pf$age)

```

## Transforming Data
```{r}

qplot(x=friend_count, data = pf)

summary(pf$friend_count)

summary(log10(pf$friend_count))

summary(log10(pf$friend_count + 1))

summary(sqrt(pf$friend_count))

```

## Install GridExtra

```{r}

##install.packages('gridExtra') 
##library(gridExtra) 

```

## Create Multiple plots in One Image Output

```{r}

p1 <- qplot(x=friend_count, data=pf)
p2 <- qplot(x=log10(friend_count + 1), data=pf)
p3 <- qplot(x=sqrt(friend_count), data=pf) 

grid.arrange(p1,p2,p3, ncol=1)


```

```{r}

p1 <- ggplot(aes(x=friend_count), data=pf) +
  geom_histogram()

p2 <- p1 + scale_x_log10()

p3 <- p1 + scale_x_sqrt()

grid.arrange(p1,p2,p3, ncol=1)

```

## Add a Scaling Layer
```{r}

logScale <- qplot(x=log10(friend_count), data=pf)

countScale <- ggplot(aes(x=friend_count), data=pf) +
  geom_histogram() +
  scale_x_log10()

grid.arrange(logScale, countScale, ncol=2)

qplot(x=friend_count, data=pf) +
  scale_x_log10()
 
```

## Frecuency Polygons (before we had histograms)
```{r}

qplot(x=friend_count, data=subset(pf,!is.na(gender)), binwidth=10) +
  scale_x_continuous(limits=c(0,1000), breaks=seq(0,1000,50)) +
  facet_wrap(~gender)

qplot(x=friend_count, y=..count../sum(..count..),
      data=subset(pf,!is.na(gender)), 
      xlab = 'Friend Count',
      ylab = 'Proportion of Users with that friend count',
      binwidth=10, geom='freqpoly', color=gender) +
  scale_x_continuous(limits=c(0,1000), breaks=seq(0,1000,50)) 

```

## Frecuency polygon to determine wich gender makes more likes

```{r}

qplot(x=www_likes, 
      data=subset(pf,!is.na(gender)), 
      xlab = 'www likes received',
      ylab = 'Proportion of likes',
      geom='freqpoly', color=gender) +
  scale_x_log10()

```

## Likes on the web solution
```{r}

by(pf$www_likes, pf$gender,sum)

```

## Histograms
```{r}

qplot(x=friend_count, data=subset(pf,!is.na(gender)),
      binwidth=25) +
  scale_x_continuous(limits=c(0,1000), breaks=seq(0,1000,50)) +
  facet_wrap(~gender)

```

## Box Plots
```{r}

qplot(x=gender, y=friend_count, data = subset(pf, !is.na(gender)), geom='boxplot')

```

```{r}

qplot(x=gender, y=friend_count, data = subset(pf, !is.na(gender)), geom='boxplot',
      ylim=c(1,1000))

```

```{r}

qplot(x=gender, y=friend_count, data = subset(pf, !is.na(gender)), geom='boxplot') +
  scale_y_continuous(limits=c(0,1000))


```


## Box Plots, Quartiles, and Friend Requests
```{r}

qplot(x=gender, y=friend_count, data = subset(pf, !is.na(gender)), geom='boxplot') +
  coord_cartesian(ylim=c(0,1000))

```

```{r}

qplot(x=gender, y=friend_count, data = subset(pf, !is.na(gender)), geom='boxplot') +
  coord_cartesian(ylim=c(0,250))

```

```{r}

by(pf$friend_count,pf$gender,summary)

```


```{r}

by(pf$friendships_initiated,pf$gender,summary)

```

```{r}

qplot(x=gender, y=friendships_initiated, data = subset(pf, !is.na(gender)), geom='boxplot') +
  coord_cartesian(ylim=c(0,150))

```

## Getting Logical

```{r}

names(pf)
summary(pf$mobile_likes)

```

```{r}
summary(pf$mobile_likes>0)

```

```{r}

mobile_check_in <- NA
pf$mobile_check_in <- ifelse(pf$mobile_likes>0,1,0)

pf$mobile_check_in <- factor(pf$mobile_check_in)

summary(pf$mobile_check_in)
 
sum(pf$mobile_check_in == 1)/length(pf$mobile_check_in)

```


